---
title: "Eric-Presentation"
author: "Eric_Wang"
date: "12/4/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(knitr.table.format = 'markdown')
library(tidyverse)
library(ggplot2)
library(dplyr)
library(readr)
Urchin_data <- read_csv("../data_raw/Urchin data - for repository.csv")
filtered_data <- select(Urchin_data, Diameter,Distance)
Compare_Wild_and_Captive <- select(Urchin_data, Diameter,Treatment)
Mean_Diameter <- Compare_Wild_and_Captive %>%
group_by(Treatment) %>%
summarize(Mean = mean(Diameter, na.rm=TRUE))
```

## Project Concept:

In this project, I will be investigating data collected from wild Urchins and captive Urchins, studying about the effect of capture and handle on their size.


## Questions to be studied 

- Does Urchin size affect the distance Urchin move in 30 seconds(predator flight response)?
- Does time after being captured affect the mean size of Urchins?

## Question 1: Does Urchin size affect the distance Urchin move in 30 seconds(predator flight response)?

```{r cars, echo = FALSE,warning=FALSE,message=FALSE}
ggplot(filtered_data)+
  geom_smooth(mapping=aes(x = Diameter, y = Distance),method="lm")+ #make the plot
scale_y_log10() +
  scale_x_log10()
```

## Question 2: Does time after being captured affect the mean size of Urchins?

```{r,echo=FALSE,warning=FALSE,message=FALSE}
ggplot(Compare_Wild_and_Captive)+
  geom_histogram(mapping=aes( x = Diameter))+
  scale_y_log10()+
  scale_x_log10()+
  facet_wrap(~Treatment)
```




## Means for each treatment group for comparison


```{r}
knitr::kable(head(Mean_Diameter))
```

##Citation
Cote, Isabelle (2019): Urchin data - for repository.csv. figshare. Dataset. https://doi.org/10.6084/m9.figshare.7302374.v1